Naturalness in U(1) extensions of the MSSM

### 2014-12-18 paper/e6ssm-tuning-paper.tex
Fixed inconsistency in notation for D-terms

(v_2^2-v_1^2)v_1+D_{H_d}v_1+\frac{\partial \Delta V_{E_6}}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\

@@

(v_2^2-v_1^2)v_2+D_{H_u}v_2+\frac{\partial \Delta V_{E_6}}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\

@@

\frac{M_Z^2}{2}=-\frac{\lambda^2s^2}{2}+\frac{\tilde{m}_{H_d}^2-\tilde{m}_{H_u}^2\tan^2\beta}{\tan^2\beta-1}+\frac{D_{H_d}-D_{H_u}\tan^2\beta}{\tan^2\beta-1},

@@

\sin 2\beta=\frac{\sqrt{2}\lambda A_{\lambda} s}{\tilde{m}_{H_d}^2+\tilde{m}_{H_u}^2+\lambda^2s^2+D_{H_d}+D_{H_u}},

@@

Written in the form of Eq. (\ref{eq:E6MZequation}) we see the potential new source of fine tuning alluded to above, in the form of the third term on the right-hand side. For large values of the VEV $s$, the $D$-term contributions can be quite a bit larger than $M_Z^2$. In particular, recent experimental limits \cite{Aad:2014cka} require that the $Z'$ mass be large, with bounds of $M_{Z'}\gtrsim 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim 2.62$ TeV in $U(1)_\chi$ models. To satisfy these limits typically requires large values of the singlet VEV $s$. For example $s\gtrsim 6$ TeV is required in the E$_6$SSM with $U(1)'=U(1)_N$, so that $|D_{H_u}|,|D_{H_d}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq 0$. As a result the remaining terms on the right-hand side of Eq. (\ref{eq:E6MZequation}) must be tuned to cancel the resulting very large contribution to $M_Z$. Moreover, because this is a large \textit{tree level} fine tuning, it may negate the increase in naturalness that is associated with having a reduced need for heavy superpartners. In $U(1)$ extended models for which $\tilde{Q}_S\neq 0$, the importance of the $Z^\prime$ mass to the fine tuning in these models can be made even clearer by writing Eq. (\ref{eq:E6MZequation}) in the form given in \cite{Athron:2013ipa},

>>>>

(v_2^2-v_1^2)v_1+D_{H_1}v_1+\frac{\partial \Delta V_{E_6}}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\

@@

(v_2^2-v_1^2)v_2+D_{H_2}v_2+\frac{\partial \Delta V_{E_6}}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\

@@

\frac{M_Z^2}{2}=-\frac{\lambda^2s^2}{2}+\frac{\tilde{m}_{H_d}^2-\tilde{m}_{H_u}^2\tan^2\beta}{\tan^2\beta-1}+\frac{D_{H_1}-D_{H_2}\tan^2\beta}{\tan^2\beta-1},

@@

\sin 2\beta=\frac{\sqrt{2}\lambda A_{\lambda} s}{\tilde{m}_{H_d}^2+\tilde{m}_{H_u}^2+\lambda^2s^2+D_{H_1}+D_{H_2}},

@@

Written in the form of Eq. (\ref{eq:E6MZequation}) we see the potential new source of fine tuning alluded to above, in the form of the third term on the right-hand side. For large values of the VEV $s$, the $D$-term contributions can be quite a bit larger than $M_Z^2$. In particular, recent experimental limits \cite{Aad:2014cka} require that the $Z'$ mass be large, with bounds of $M_{Z'}\gtrsim 2.51$ TeV in $U(1)_\psi$ models and $M_{Z'}\gtrsim 2.62$ TeV in $U(1)_\chi$ models. To satisfy these limits typically requires large values of the singlet VEV $s$. For example $s\gtrsim 6$ TeV is required in the E$_6$SSM with $U(1)'=U(1)_N$, so that $|D_{H_1}|,|D_{H_2}|\gg M_Z^2$ for $E_6$ models with $\tilde{Q}_S\neq 0$. As a result the remaining terms on the right-hand side of Eq. (\ref{eq:E6MZequation}) must be tuned to cancel the resulting very large contribution to $M_Z$. Moreover, because this is a large \textit{tree level} fine tuning, it may negate the increase in naturalness that is associated with having a reduced need for heavy superpartners. In $U(1)$ extended models for which $\tilde{Q}_S\neq 0$, the importance of the $Z^\prime$ mass to the fine tuning in these models can be made even clearer by writing Eq. (\ref{eq:E6MZequation}) in the form given in \cite{Athron:2013ipa},
